\renewcommand{\nomebreve}{io\_std}
\renewcommand{\titolo}{Receiving input and sending output on the standard channels}

\mbox{\ }
\vspace{-1.9cm}

\introduzione{}

Your program should take in an integer number as its input
and output the very same number, no elaboration is required  
(this is a start up exercise to get into the system).

The input will simply take place from \texttt{stdin}, and, similarly,
the output will occur on \texttt{stdout}.
You do not need to open and manage any file.
Once lounched, your program will be fed with one single integer from \texttt{stdin} and is required to return the very same integer on \texttt{stdout}. 

   
% Esempi
\sezionetesto{input/output example}
\esempio{17}{17}

% Assunzioni
\sezionetesto{Assumptions}
\begin{itemize}[nolistsep, noitemsep]
  \item the absolute value of the input number is at most $1000$.
        Therefore, the number can be conveniently stored within the standard variables offered by your preferred programming language (like a C or c++ variable of type \texttt{int}, or an \texttt{integer} variable in Pascal).
\end{itemize}
  
  \section*{Subtasks}
  \begin{itemize}
    \item \textbf{Subtask 1 [30 punti]:} your program is required to work correctly at least on the example of the test (you do not even need to read the input).
    \item \textbf{Subtask 2 [30 punti]:} the number your program receives in input is $13$.
    \item \textbf{Subtask 3 [40 punti]:} no special restriction (beyond the one on the maximum absolute value given in the general ``Assumptions'' section).
  \end{itemize}


  \section*{General notes on the submission system (with evaluation and immediate feedback) of your solutions}

You are required to submit only the text file of the source code of your program.
Our server will compile your source code with the compiler suggested by the extension of your file, according to the following table.

\vspace{0.2cm}
\begin{tabular}{|l|l|l|}
\hline
  programming language & file extension & compiler/interpreter employed by the server  \\ \hline
\hline               
  python  & .py  & python3 \\ \hline
  bash    & .sh  & bash \\ \hline
  c++     & .cpp & g++ \\ \hline
  C       & .c   & gcc \\ \hline
  Pascal  & .pas & fpc \\ \hline
\hline               
\end{tabular}
\vspace{0.2cm}

We advice you to test your solution in local before submitting it.
In case you suspect that the remote behaviour of your submission differs from what in local, the exact compiling options employed by the server in compling your source code are reported on the page of the problem on the site of the contest.
